### 2020-04-01 Paper_EV/Paper_EV.tex
Backup update 01_04

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
% TODO:
% - Title page: Dr. -> Dr. ir.
% - Acronyms, right order of full and short appearences
% - Create List of Symbols
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

% Package for setting up the list of symbols
%https://tex.stackexchange.com/questions/112884/how-to-achieve-nomenclature-entries-like-symbol-description-dimension-and-uni
\usepackage{nomencl,etoolbox,ragged2e,siunitx}
%
\newcommand{\DimensUnits}[2]{\makebox[1em]{#1}\makebox[4em]{#2\hfill}\ignorespaces}
\newcommand{\insertnomheaders}{\item[\bfseries Symbol]\DimensUnits{}{\textbf{Unit}}\textbf{Description}}
%
\renewcommand\nomgroup[1]{%
  \item[\large\bfseries
  \ifstrequal{#1}{A}{Acronyms}{%
  \ifstrequal{#1}{B}{Latin Letters}{%
  \ifstrequal{#1}{G}{Greek Letters}{%
  \ifstrequal{#1}{S}{Indices}{% 
  \ifstrequal{#1}{U}{Subscripts}{%   
  \ifstrequal{#1}{X}{Other Symbols}{}}}}}}]
  \insertnomheaders
  }
%
\renewcommand*{\nompreamble}{\markboth{\nomname}{\nomname}}
% parbox - Description
\newcommand{\nomdescr}[1]{\parbox[t]{10cm}{\RaggedRight #1}}
\newcommand{\nomwithdim}[5]{\nomenclature[#1]{#2}{\DimensUnits{}{#5}\nomdescr{#3}}}
%
\makenomenclature

@@

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}

% Add Table of Symbols
%\chapter*{Table of Symbols} \label{sec:symbols}
\mbox{}
\nomwithdim{B}{\( \bm{F} \)}{Force}{L}{$N$}
\nomwithdim{B}{\( g \)}{Gravitational acceleration}{}{$m/s^2$}
\nomwithdim{G}{\( \alpha \)}{Angle of attack}{}{$rad$}
\nomwithdim{G}{\( \zeta \)}{Damping of a linear second order system}{}{--}
\nomwithdim{S}{\( m \)}{Variable related to pitch moment}{}{}
\nomwithdim{S}{\( W \)}{Wind}{}{}
\renewcommand{\nomname}{Table of Symbols}
\printnomenclature[6em]

% Manually add Chapter names to the header (per default not included by Latex)
\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

%Insert empty page after table of symbols
\newpage\null\thispagestyle{empty}\newpage

@@

As it was shown in Chapter \ref{cha:theoretical_background} (see Figures \ref{fig:indi_inner_croped} and \ref{fig:indi_outer_croped}), the inner and outer loops employ several second order filters. The main task of two of them is to reduce  noise in the measurements of the angular and linear acceleration. Other filters are applied to remaining feedback quantities. Using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time. The general transfer function of a second order filter in continuous domain is defined by the following formula
\begin{equation}
	\begin{split}
		F(s) = \frac{\omega_n^2}{s^2+2\zeta\omega_ns+\omega_n^2}
		\label{eq:filter_c}
	\end{split}
\end{equation}
with the relative damping coefficient $\zeta$ and the eigenfrequency $\omega_n$. To implement transfer function from Equation \ref{eq:filter_c} on a digital computer it must be transformed to the discrete domain. To perform this transformation \textit{bilinear transformation} (also called \textit{Tustin-Transformation}) was used. Using the bilinear transformation (with frequency warping technique), the mapping relation between $s$ and $z$ results in
\begin{equation}
	\begin{split}
		s \ \widehat{=} \ \frac{\omega_n}{\tan(\omega_n\frac{T_S}{2})} \frac{1-z^{-1}}{1+z^{-1}}
		\label{eq:filter_c}
	\end{split}
\end{equation}
Thus, the discrete version of the Equation \ref{eq:filter_c} is:
\begin{equation}
	\begin{split}
		F(z) = \frac{n_0 + n_1z^{-1} + n_2z^{-2}}{d_0 + d_1z^{-1} + d_2z^{-2}}
		\label{eq:filter_d}
	\end{split}
\end{equation}
where 
\begin{subequations}
	\begin{align}
		n_0 &= 1 \\
		n_1 &= 2\\
		n_2 &= 1 \\
		d_0 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1 \\
		d_1 &= -\frac{2}{\tan^2(\omega_n\frac{T_S}{2})} + \frac{4\zeta}{\tan(\omega_n\frac{T_S}{2})} \\
		d_2 &= \frac{1}{\tan^2(\omega_n\frac{T_S}{2})} - \frac{2\zeta}{\tan(\omega_n\frac{T_S}{2})} + 1
	\end{align}
	\label{eq:filter_parameters}
\end{subequations}

@@

As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance. Matrix $G_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$. Since $I_{rzz}$ is small, it was expected that $G_2$ will not have a big impact on the model response. Figure \ref{fig:g2_comp} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers. 
\begin{figure}[H]
	\centering 
	\begin{tikzpicture}
		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
		\includegraphics[width=0.85\textwidth]{figs/sim_outer_all.pdf}};
	\end{tikzpicture}
	% Figure description is centered aligned
	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
	\caption[Response of the outer loop simulation model to a step input.]{Response of the outer loop simulation model to a step input. Blue lines represent reference values, red lines denote measured values.}
	\label{fig:sim_outer_all}
\end{figure}
\begin{figure}[H]
	\centering 
	\begin{tikzpicture}
		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
		\includegraphics[width=0.85\textwidth]{figs/sim_inner_all.pdf}};
	\end{tikzpicture}
	% Figure description is centered aligned
	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
	\caption[Response of the inner loop simulation model to the input provided by the outer loop]{Response of the inner loop simulation model to the input provided by the outer loop. Blue lines represent reference values, red lines denote measured values.}
	\label{fig:sim_inner_all}
\end{figure}It can be seen that both responses are almost the same. In the next section, (see \ref{subsec:parameter_estimation_inner}) through the estimation of the control effectiveness terms using the flight data, this observation will be practically confirmed. In practice, considering only important terms, can reduce the implementation effort of a particular control algorithm.

@@

By making use of the finite difference approximation, Equation \ref{eq:t_tilde_est_cmd} can be rewritten as
\begin{equation}
	\dot{T}_{cmd} = \ddot{v}_{z} K_{cmd}^{-1}
	\label{eq:t_tilde_est_cmd_diff}
\end{equation}
where $T_{cmd}$ is the commanded thrust, and $\dot{v}_{z}$ the linear acceleration along the $z$-axis. Both values can be obtained from the flight data. Similarly to subsection \ref{subsec:parameter_estimation_inner}, differentiating will amplify high-frequency portion of the signal and contribute to the elimination of the bias. Note that to obtain realistic course of the commanded thrust values, just before the differentiation, these values have to be passed through the actuator dynamics model $A'(s)$. Equation \ref{eq:t_tilde_est_cmd_diff} has then the following form 
\begin{equation}
	\dot{T}_{cmd, a} = \ddot{v}_{z} K_{cmd}^{-1}
	\label{eq:t_tilde_est_cmd_diff_actuator}
\end{equation}
where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.

>>>>

% This is one possible realization of the official FSD Microsoft Word template. The title page has to be filled in in Microsoft Word environment and saved as a PDF file. Note, that in the header and footer the name of the author and the thesis topic have to be provided. 
%
% Compile Template in following order:
%
% pdflatex Paper_EV
% makeindex Paper_EV.nlo -s nomencl.ist -o Paper_EV.nls (Table of Symbols)
% makeindex Paper_EV.acn -s Paper_EV.ist -t Paper_EV.alg -o Paper_EV.acr (Table of Acronyms)
% makeindex Paper_EV.glo -s Paper_EV.ist -t Paper_EV.glg -o Paper_EV.gls
% pdflatex Paper_EV
% pdflatex Paper_EV
%
%
%#################################################################################
%#################################################################################
%#################################################################################

@@

@@

%Insert empty page after table of acronyms
\newpage\null\thispagestyle{empty}\newpage

% Manually add Chapter names to the header (per default not included by Latex) 
\protect\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

\chapter*{Table of Symbols} \label{sec:table_of_symbols}

\textbf{Latin Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $A(s),~A(z)$ & -- & Transfer function of the actuator dynamics \\ 
    $A'(s),~A'(z)$ & -- & Transfer function of the actuator dynamics model \\
    $a(t)$ & -- & Function of the first order lag element in time domain \\
    $b$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $d$ & $m/s^2$ & Disturbance \\
    $d_0, d_1, d_2$ & -- & Denominator coefficients of the discrete second order filter \\
    $E(t)$ & -- & Objective function \\
    $\bm{F}$ & $N$ & Force vector \\
    $\bm{F}_A$ & $N$ & Aerodynamic force vector \\
    $\bm{F}_G$ & $N$ & Gravitational force vector \\
    $\bm{F}_P$ & $N$ & Propulsive force vector \\
    $\bm{f}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{G}$ & -- & Control effectiveness matrix of the outer loop \\
    $\bm{G}_1$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_2$ & -- & Control effectiveness matrix of the inner loop \\
    $\bm{G}_{inner}$ & -- & Dynamics matrix of the inner loop \\
    $\bm{G}_{outer}$ & -- & Dynamics matrix of the outer loop \\
    $\bm{G}(x)$ & -- & Input matrix \\
    $g$ & $m/s^2$ & Gravitational acceleration \\
    $H(s),~H(z)$ & -- & Transfer function of the second order filter \\
    $\bm{h}(\bm{x})$ & -- & Nonlinear vector field \\
    $\bm{I}$ & $Nm^2$ & Inertia tensor of the quadrotor \\
    $\bm{I_{rzz}}$ & $Nm^2$ & $zz$-element of the inertia tensor of the rotor \\
    $i$ & -- & Relative degree of the dynamic system \\
    $K$ & -- & Compensation gain \\
    $K_{cmd}$ & -- & Thrust mapping parameter \\
    $k$ & $kg/s$ & Drag coefficient \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  %\captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_1}
\end{table}

% Manually add Chapter names to the header (per default not included by Latex) 
\protect\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $k$ & -- & Gain of the actuator dynamics \\ 
    $k_F$ & $\frac{N}{rad/s}$ & Force constant of the rotors \\
    $k_M$ & $\frac{Nm}{rad/s}$ & Moment constant of the rotors \\
    $L$ & -- & Lie derivative operator \\
    $l$ & $m$ & Lever arm of the rotors to the C.G. along the body $y$-axis \\
    $\bm{M}$ & $Nm$ & Moment vector \\
    $\bm{M}_A$ & $Nm$ & Aerodynamic Moment vector \\
    $\bm{M}_c$ & $Nm$ & Control moment vector \\
    $\bm{M}_G$ & $Nm$ & Gravitational Moment vector \\
    $\bm{M}_{gyro}$ & $Nm$ & Moment vector due to the gyroscopic effects of the rotor \\
    $\bm{M}_{OB}$ & -- & Transformation matrix from the body-fixed into NED frame \\
    $\bm{M}_P$ & $Nm$ & Propulsion moment vector \\
    $m$ & $kg$ & Mass of the quadrotor \\
    $m_{cf}$ & $kg$ & Mass of the Crazyflie quadrotor \\
    $m_r$ & $kg$ & Additional mass (disturbance \\
    $n$ & -- & Number of samples \\
    $n_0, n_1, n_2$ & -- & Numerator coefficients of the discrete second order filter \\
    $P$ & -- & Parameter \\
    $p$ & $rad/s$ & Roll rate \\ 
	$q$ & $rad/s$ & Pitch rate \\
    $r$ & $rad/s$ & Yaw rate \\
	$s$ & -- & Laplace variable \\
    $T$ & $N$ & Thrust \\
	$T$ & $s$ & Time constant of the actuator dynamics \\
    $T_{cmd}$ & -- & Thrust in motor units \\
	$T_s$ & $s$ & Sample time of the controller \\
    $\tilde{T}$ & $N$ & Thrust increment\\
	$t$ & $s$ & Time \\    
    $u$ & -- & Input vector \\
    $\bm{u}_c$ & -- & Control vector \\
    $u$ & $m/s$ & $x$-component of the velocity vector \\ %[0.5ex]
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_2}
\end{table}

% Manually add Chapter names to the header (per default not included by Latex) 
\protect\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    $V$ & $m/s$ & Component of the velocity vector \\ 
    $v$ & $m/s$ & $y$-component of the velocity vector \\
    $ \bm{v}$ & $m/s$ & Velocity vector \\
    $W$ & $N$ & Weight of the quadrotor \\
    $w$ & $m/s$ & $z$-component of the velocity vector \\
    $\bm{x}$ & -- & State vector \\
    $x$ & $m$ & Position coordinate in $x$-direction \\
    $\bm{y}$ & -- & Output vector \\
    $y$ & $m$ & Position coordinate in $y$-direction \\
    $\bm{z} $ & -- & Transformed state vector \\
    $z$ & -- & z-Transformation variable \\
    $z$ & $m$ & Position coordinate in $z$-direction \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_latin_3}
\end{table}

% Manually add Chapter names to the header (per default not included by Latex) 
\protect\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

\textbf{Greek Letters}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{1.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Unit} & \textbf{Description} \\ [1.2ex] 
    $\alpha$ & -- & Parameter of the discrete first order lag element \\ 
    $\zeta$ & -- & Relative damping coefficient of the second order filter \\
    $\bm{\eta}$ & $rad$ & Attitude vector \\
    $\Theta$ & $rad$ & Pitch angle \\
    $\tilde{\Theta}$ & $rad$ & Pitch angle increment \\
    $\Theta_c$ & $rad$ & Control pitch angle \\
    $\bm{\nu}$ & -- & Virtual control input vector \\
    $\bm{\nu}_{\bm{\dot{v}}}$ & $m/s^2$ & Virtual control input vector of the outer loop \\
    $\bm{\nu}_{\bm{\dot{\omega}}}$ & $rad/s^2$ & Virtual control input vector of the inner loop \\
    $\bm{\xi}$ & $m$ & Position vector \\
    $\Phi$ & $rad$ & Roll/Bank angle \\
    $\tilde{\Phi}$ & $rad$ & Roll angle increment \\
    $\Phi_c$ & $rad$ & Control roll angle \\
	$\bm{\phi}(\bm{x})$ & -- & State transformation function \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_greek}
\end{table}

\textbf{Indices}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
    $0$ & Initial point in time \\ 
    $a$ & Passed through the actuator dynamics \\ 
    $B$ & Body-fixed coordinate frame \\ 
    $D$ & Down \\
    $E$ & East \\ 
    $f$ & Filtered \\ 
    $G$ & Center of gravity \\ 
    $G$ & Gravitational \\
    $K$ & Kinematic coordinate frame \\
    $N$ & North \\
    $O$ & North-East-Down coordinate frame \\
    $R$ & Reference point \\
    $x$ & $x$-component of a variable \\
	$y$ & $y$-component of a variable \\
	$z$ & $z$-component of a variable \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_indices}
\end{table}

\textbf{Other Symbols}
% Add table ([...ex] adds some extra vertical spacing after corresponding row)
\begin{table}[H]
  %\centering
  \begin{tabular}{p{2.5cm} p{10cm}} 
    \textbf{Symbol} & \textbf{Description} \\ [1.2ex] 
    $L$ & Lie derivative operator \\ 
	$\nabla$ & Nabla-Operator \\ %[0.5ex]  
  \end{tabular}
  %\caption[Sample table 1]{Sample table 1}  
  \captionsetup{font=bf, belowskip=-0.5cm}
  \label{table:tab_other_symbols}
\end{table}

% Manually add Chapter names to the header (per default not included by Latex) 
\protect\thispagestyle{fancy_beginning}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\chaptermark{Table of Symbols}

%Insert empty page after table of symbols
\newpage

@@

As it was shown in Chapter \ref{cha:theoretical_background} (see Figures \ref{fig:indi_inner_croped} and \ref{fig:indi_outer_croped}), the inner and outer loops employ several second order filters. The main task of two of them is to reduce  noise in the measurements of the angular and linear acceleration. Other filters are applied to remaining feedback quantities. Using the same parameters for every filter, this technique accounts for the time delay which is introduced by the filters and ensures that all quantities that were fed back are from the same point in time. The general transfer function of a second order filter in continuous domain is defined by the following formula
\begin{equation}
	\begin{split}
		H(s) = \frac{\omega_n^2}{s^2+2\zeta\omega_ns+\omega_n^2}
		\label{eq:filter_c}
	\end{split}
\end{equation}
with the relative damping coefficient $\zeta$ and the eigenfrequency $\omega_n$. To implement transfer function from Equation \ref{eq:filter_c} on a digital computer it must be transformed to the discrete domain. To perform this transformation \textit{bilinear transformation} (also called \textit{Tustin-Transformation}) was used. Using the bilinear transformation (with frequency warping technique), the mapping relation between $s$ and $z$ results in
\begin{equation}
	\begin{split}
		s \ \widehat{=} \ \frac{\omega_n}{\tan(\omega_n\frac{T_s}{2})} \frac{1-z^{-1}}{1+z^{-1}}
		\label{eq:filter_c}
	\end{split}
\end{equation}
Thus, the discrete version of the Equation \ref{eq:filter_c} is:
\begin{equation}
	\begin{split}
		H(z) = \frac{n_0 + n_1z^{-1} + n_2z^{-2}}{d_0 + d_1z^{-1} + d_2z^{-2}}
		\label{eq:filter_d}
	\end{split}
\end{equation}
where 
\begin{subequations}
	\begin{align}
		n_0 &= 1 \\
		n_1 &= 2\\
		n_2 &= 1 \\
		d_0 &= \frac{1}{\tan^2(\omega_n\frac{T_s}{2})} + \frac{2\zeta}{\tan(\omega_n\frac{T_s}{2})} + 1 \\
		d_1 &= -\frac{2}{\tan^2(\omega_n\frac{T_s}{2})} + \frac{4\zeta}{\tan(\omega_n\frac{T_s}{2})} \\
		d_2 &= \frac{1}{\tan^2(\omega_n\frac{T_s}{2})} - \frac{2\zeta}{\tan(\omega_n\frac{T_s}{2})} + 1
	\end{align}
	\label{eq:filter_parameters}
\end{subequations}

@@

As mentioned in the beginning of this chapter, a simulation can be used to determine terms of the model which have a greater influence on the overall controller performance. Matrix $\bm{G}_2$ of the control effectiveness term in Equation \ref{eq:indi_inner_control_law} contains only the term of the inertia tensor of the propeller $I_{rzz}$. Since $I_{rzz}$ is small, it was expected that $\bm{G}_2$ will not have a big impact on the model response. Figure \ref{fig:g2_comp} confirms this expectation, by plotting the step response of the Crazyflie model with and without considering  the gyroscopic effects of the quadrotor propellers. 
\begin{figure}[H]
	\centering 
	\begin{tikzpicture}
		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
		\includegraphics[width=0.85\textwidth]{figs/sim_outer_all.pdf}};
	\end{tikzpicture}
	% Figure description is centered aligned
	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
	\caption[Response of the outer loop simulation model to a step input.]{Response of the outer loop simulation model to a step input. Blue lines represent reference values, red lines denote measured values.}
	\label{fig:sim_outer_all}
\end{figure}
\begin{figure}[H]
	\centering 
	\begin{tikzpicture}
		\node[inner sep=0pt] (crazyflie_drone) at (0,0) {
		\includegraphics[width=0.85\textwidth]{figs/sim_inner_all.pdf}};
	\end{tikzpicture}
	% Figure description is centered aligned
	\captionsetup{justification=centering, singlelinecheck=off, font=bf, belowskip=-0.5cm}
	\caption[Response of the inner loop simulation model to the input provided by the outer loop]{Response of the inner loop simulation model to the input provided by the outer loop. Blue lines represent reference values, red lines denote measured values.}
	\label{fig:sim_inner_all}
\end{figure}It can be seen that both responses are almost the same. In the next section, (see \ref{subsec:parameter_estimation_inner}) through the estimation of the control effectiveness terms using the flight data, this observation will be practically confirmed. In practice, considering only important terms, can reduce the implementation effort of a particular control algorithm.

@@

By making use of the finite difference approximation, Equation \ref{eq:t_tilde_est_cmd} can be rewritten as
\begin{equation}
	\dot{T}_{cmd} = \ddot{v}_{z} K_{cmd}^{-1}
	\label{eq:t_tilde_est_cmd_diff}
\end{equation}
where $T_{cmd}$ is the commanded thrust, and $\dot{v}_{z}$ the linear acceleration along the $z$-axis. Both values can be obtained from the flight data. Similarly to subsection \ref{subsec:parameter_estimation_inner}, differentiating will amplify high-frequency portion of the signal and contribute to the elimination of the bias. Note that to obtain realistic course of the commanded thrust values, just before the differentiation, these values have to be passed through the actuator dynamics model $A'(s)$. Equation \ref{eq:t_tilde_est_cmd_diff} has then the following form 
\begin{equation}
	\dot{T}_{cmd, a} = \ddot{v}_{z} K_{cmd}^{-1}
	\label{eq:t_tilde_est_cmd_diff_actuator}
\end{equation}
–––where $T_{cmd, a}$ is the thrust value filtered with the actuator dynamics model. The least squares approach is then be applied to obtain $K_{cmd}$.
